Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-22 paper/paper.tex
Update

\begin{description}
  \item[Concept:] indentifies a rel willevant term, concept, idea, in the knowledge domain of the sentence.
  \item[Action:] indentifies a process or modification of other entities. It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition), where it denotes the act of being exposed to the Sun, and “daños” (damages), where it denotes the act of damaging the skin. It can also be used to indicate non-verbal functional relations, such as “padre” (parent), etc.
  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) with some additional arguments such as “60 años” (60 years).
  \item[Reference:] identifies a textual element that refers to an entity –of the same sentence or of different one–, which can be indicated by textual clues such as “esta”, “aquel”, etc.
\end{description}

@@

\paragraph{General relations (6)} are general-purpose relations between two concepts (it involves Concept, Action, Predicate, and Reference) that have a specific semantic. When any of these relations applies, it is preferred over a domain relation –tagging a key phrase as a link between two information units–, since their semantic is independent of any textual label:

@@

\paragraph{Contextual relations (3)} allow to refine an entity (it involves Concept, Action, Predicate, and Reference) by attaching modifiers. These are:

\begin{description}
  \item[in-time:] to indicate that something exists, occurs or is confined to a time-frame, such as in “exposición” in-time “verano”.
  \item[in-place:] to indicate that something exists, occurs or is confined to a place or location.
  \item[in-context:] to indicate a general context in which something happens, like a mode, manner, or state, such as “exposición” in-context “prolongada”.
\end{description}

@@

\begin{description}
  \item[subject:] indicates who performs the action, such as in “[el] asma afecta […]”.
  \item[target:] indicates who receives the effect of the action, such as in “[…] afecta [las] vías respiratorias”. Actions can have several subjects and targets, in which case the semantic interpreted is that the union of the subjects performs the action over each of the targets.
\end{description}

@@

\begin{description}
  \item[domain:] indicates the main entity on which the predicate applies.
  \item[arg:] indicates an additional entity that specifies a value for the predicate to make sense. The exact semantic of this argument depends on the semantic of the predicate label, such as in “mayores [de] 60 años”, where the predicate label “mayores” indicates that “60 años” is a quantity, that restricts the minimum age for the predicate to be true.
\end{description}

@@

@@

\begin{table*}
  \resizebox{\textwidth}{!}{
  \begin{tabular}{l|ccc|ccc|ccc}
    \toprule
    & \multicolumn{3}{c|}{\textbf{Main}} & \multicolumn{3}{c|}{\textbf{Task A}} & \multicolumn{3}{c}{\textbf{Task B}} \\
    \textbf{Team}    & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$ \\
    \midrule
    Vicomtech        & \bf 0.531 & 0.540 & 0.534 & 0.684 & 0.699 & \bf 0.747 & 0.371 & \bf 0.541 & 0.283 \\
    PUCRJ-PUCPR-UFMG & 0.528 & \bf 0.568 & 0.502 & \bf 0.706 & \bf 0.714 & 0.697 & 0.263 & 0.366 & 0.205 \\
    IXA              & 0.498 & 0.464 & \bf 0.538 & 0.653 & 0.613 & 0.698 & \bf 0.430 & 0.453 & \bf 0.409 \\
    uhKD4            & 0.422 & 0.485 & 0.374 & 0.527 & 0.517 & 0.537 & 0.317 & 0.556 & 0.222 \\
    UH-MMM           & 0.338 & 0.291 & 0.403 & 0.607 & 0.546 & 0.685 & 0.053 & 0.077 & 0.041 \\
    Codestrange      & 0.232 & 0.337 & 0.176 & 0.080 & 0.415 & 0.044 & 0.032 & 0.437 & 0.017 \\
    JAD              & 0.109 & 0.234 & 0.071 & 0.262 & 0.315 & 0.224 & 0.007 & 0.375 & 0.003 \\
    GuanZhengyi      & -     & -     & -     & 0.334 & 0.520 & 0.245 & -     & -     & -     \\
    Maoqin           & -     & -     & -     & 0.173 & 0.271 & 0.127 & -     & -     & -     \\
    \midrule
    \it human        & 0.644 & 0.673 & 0.618 & 0.831 & 0.862 & 0.802 & 0.621 & 0.596 & 0.647 \\
    \it baseline     & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
    \bottomrule
  \end{tabular}}

  \caption{Summary of results in the three evaluation scenarios of the eHealth-KD Challenge. The top result in every metric is highlighted. For comparative purpose, an estimated \textit{human} performance~(based on inter-annotator agreement) and a simple computational \textit{baseline} are also reported.\label{tab:results}}
\end{table*}

>>>>

\begin{description}
  \item[Concept:] indentifies a rel willevant term, concept, idea, in the knowledge domain of the sentence.
  \item[Action:] indentifies a process or modification of other entities. It can be indicated by a verb or verbal construction, such as “afecta” (affects), but also by nouns, such as “exposición” (exposition) and “daños” (damages).
  \item[Predicate:] identifies a function or filter of another set of elements, which has a semantic label in the text, such as “mayores” (older), and is applied to an entity, such as “personas” (people) withsome additional arguments such as “60 años” (60 years).
  \item[Reference:] identifies a textual element that refers to an entity --of the same sentence or of different one--, which can be indicated by textual clues such as “esta”, “aquel”, etc.
\end{description}

@@

\paragraph{General relations (6)} are general-purpose relations between two entities that have a pre-defined semantic:

@@

\paragraph{Contextual relations (3)} allow to refine an entity by attaching modifiers:

\begin{description}
  \item[in-time:] to indicate that something exists, occurs or is confined to a time-frame.
  \item[in-place:] to indicate that something exists, occurs or is confined to a place or location.
  \item[in-context:] to indicate a general context in which something happens, like a mode, manner, or state.
\end{description}

@@

\begin{description}
  \item[subject:] indicates who performs the action.
  \item[target:] indicates who receives the effect of the action.
\end{description}

@@

\begin{description}
  \item[domain:] indicates the main entity on which the predicate applies.
  \item[arg:] indicates an additional entity that specifies a value for the predicate to make sense.
\end{description}

@@

\begin{table*}
  \resizebox{\textwidth}{!}{
  \begin{tabular}{l|ccc|ccc|ccc}
    \toprule
    & \multicolumn{3}{c|}{\textbf{Main}} & \multicolumn{3}{c|}{\textbf{Task A}} & \multicolumn{3}{c}{\textbf{Task B}} \\
    \textbf{Team}    & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$ \\
    \midrule
    Vicomtech        & \bf 0.531 & 0.540 & 0.534 & 0.684 & 0.699 & \bf 0.747 & 0.371 & \bf 0.541 & 0.283 \\
    PUCRJ-PUCPR-UFMG & 0.528 & \bf 0.568 & 0.502 & \bf 0.706 & \bf 0.714 & 0.697 & 0.263 & 0.366 & 0.205 \\
    IXA              & 0.498 & 0.464 & \bf 0.538 & 0.653 & 0.613 & 0.698 & \bf 0.430 & 0.453 & \bf 0.409 \\
    uhKD4            & 0.422 & 0.485 & 0.374 & 0.527 & 0.517 & 0.537 & 0.317 & 0.556 & 0.222 \\
    UH-MMM           & 0.338 & 0.291 & 0.403 & 0.607 & 0.546 & 0.685 & 0.053 & 0.077 & 0.041 \\
    Codestrange      & 0.232 & 0.337 & 0.176 & 0.080 & 0.415 & 0.044 & 0.032 & 0.437 & 0.017 \\
    JAD              & 0.109 & 0.234 & 0.071 & 0.262 & 0.315 & 0.224 & 0.007 & 0.375 & 0.003 \\
    GuanZhengyi      & -     & -     & -     & 0.334 & 0.520 & 0.245 & -     & -     & -     \\
    Maoqin           & -     & -     & -     & 0.173 & 0.271 & 0.127 & -     & -     & -     \\
    \midrule
    \it human        & 0.644 & 0.673 & 0.618 & 0.831 & 0.862 & 0.802 & 0.621 & 0.596 & 0.647 \\
    \it baseline     & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
    \bottomrule
  \end{tabular}}
    \caption{Summary of results in the three evaluation scenarios of the eHealth-KD Challenge. The top result in every metric is highlighted. For comparative purpose, an estimated \textit{human} performance~(based on inter-annotator agreement) and a simple computational \textit{baseline} are also reported.\label{tab:results}}
  \end{table*}

@@
